Manual classification of tumor cells

### 2024-05-01 analyses/ewings-cell-type/01-marker-gene-tumor-classification.Rmd
save tumor normal classifications

```{r paths}
# Input files
sce_filename <- glue::glue("{params$library_id}_processed_annotated.rds")
sce_file <- file.path(sample_dir, sce_filename)

marker_genes <- file.path(module_base, "references", "tumor-marker-genes.tsv")
```

@@

>>>>

```{r paths}
# Input files
sce_filename <- glue::glue("{params$library_id}_processed.rds")
sce_file <- file.path(sample_dir, sce_filename)

marker_genes <- file.path(module_base, "references", "tumor-marker-genes.tsv")

# output tumor/normal classifications
results_dir <- file.path(module_base, "results", "marker_gene_analysis")
fs::dir_create(results_dir)

classifications_filename <- glue::glue("{params$library_id}_tumor_normal_classifications.tsv")
output_classifications_file <- file.path(results_dir, classifications_filename)
```

@@

## Save outputs

```{r}
# get a dataframe with barcodes, sum_classification and cluster_classification 
celltype_classification_df <- celltype_classification_df |> 
  dplyr::select(
    barcodes,
    marker_gene_classification = sum_classification, 
    cluster_classification
  )

readr::write_tsv(celltype_classification_df, output_classifications_file)
```
